
```{r 'check_ps', include=FALSE}

user.name = '' # set to your user name

# To check your problem set, run the 
# RStudio Addin 'Check Problemset'

# Alternatively run the following lines
library(RTutor)
ps.dir = getwd() # directory of this file
ps.file = 'Logit.Rmd' # name of this file
check.problem.set('Logit', ps.dir, ps.file, user.name=user.name, reset=FALSE)
```

# Logit/Probit Regression

Welcome




## Exercise 2: Check -- Check the data

We will check the data set. Each exercise are created so they do not depend on the previous one. So we will first need to import the data again. To be sure, you remember the commands, you will need to import the data again.

**Task:** Import the data from `wells.xlsx` and save them in a data.frame named `wells`. In a second line of code, use the command `head` to view the first records of the data frame you have just created

```{r "2__Check"}
# replace the #... with your codes
# ...
# ...
```

#### Transform binary variables into factor

To facilitate data analysis, we will transform some of the variables. The first transformation is to change the variable `switch`, currently a numeric variable into a factor variable. (Click on the info button just below if you do not know what a factor is)

info("Factors") # Run this line (Strg-Enter) to show info

**Task**: 

1. Create a new factor by converting the numerical variable `switch` into a factor variable, where the labels of the levels are changed according to the rule 1 -> "Changed", 0 -> "Kept", and will be used in that order. Name your newly created variable `changed`

2. View the first values of the variable to check the results obtained

```{r "2__Check__2"}
# type your commands here
```

#### Summarize the data

info("`summary` applied to a data.frame object") # Run this line (Strg-Enter) to show info

The command `summary` is helpful to get a rapid overview of the data.

```{r "2__Check__4"}
# type your command
```

### Making plots

#### One variable plot 

Another way to check the data that you will be using is to draw some plots to identify potential outliers. The easiest way to do this is to use the function `plot()` with one variable.

*Task* :  Plot the variable `arsenic` 

```{r "2__Check__5"}
# type your command
```

#### Two variables scatterplot 

*Task* :  Plot the variable `arsenic` against the variable  `dist` 

```{r "2__Check__6"}
# type your command
```


### Graphical examination of the relations

We want to know how the decision to switch (the response variable) is related to some exogenous/explanatory variables (arsenic, dist, assoc and educ). It is good practice to begin with some simple graphical examination of the data before undertaking any formal modelling. 


info("spine plots and spinograms") # Run this line (Strg-Enter) to show info


As an exercise you will create spinogram to visualize how the proportions of factor variable `change`  evolve with the numerical variables `dist`. 

**Task:**  Construct the spinogram of the dependent variable `changed` and the independent variable `dist`. To do this, follow the example given *spine plots and spinograms* info box.


```{r "2__Check__9"}
# type your command here
```

**Quiz**

#! addon__quiz__Interpret a spinogram


Write your answer text inside the quotes " " as an R String and press `Check`.
(Note that you always see afterwards the message "Great, solved correctly."
 But your answer will in fact be graded after you submit your problem set.)
   
